Model LF

### 2022-10-07 max_dp endogen stød.Rmd
Commit

>>>>

```{r}
plot(((yk_ds_07 - yk_ds_00) / yk_ds_00), col= "blue", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp");
lines(((yk_ds_06 - yk_ds_00) / yk_ds_00), col= "black");
lines(((yk_ds_05 - yk_ds_00) / yk_ds_00), col= "red");
legend("left", legend=c("Scenario 4","Scenario 3","Scenairo 2"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red"));
grid()

plot(((ur_ds_07 - ur_ds_00) / ur_ds_00), col= "blue", xlab= "Year", ylab= "% Change in UR", main= "UR");
lines(((ur_ds_06 - ur_ds_00) / ur_ds_00), col= "black");
lines(((ur_ds_05 - ur_ds_00) / ur_ds_00), col= "red");
legend("left", legend=c("Scenario 4","Scenario 3","Scenairo 2"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red"));
grid()
```
